---
title: "Milk Analysis"
author: "Gustavo Reyes"
date: "10/25/2021"
output: html_document
---
#Milk Analysis: 

```{r}
#Setting Working Directory-------------------------------------
#setwd("C:/Users/gareyes3/Documents/GitHub/Share-Table-Milk/R") 
#setwd("G:/Share Table QMRA/Share-Table-QMRA/R")
#setwd(getSrcDirectory()[1])
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) #Set working directory to the path of document
```

##Loading Libraries
```{r ,echo=FALSE}
#Opening Libary and Inputs-------------------------------------
source("Util_Library.R")
source("Functions_Full_Analysis.R")
```


##Loading Model Necessary Inputs. 
```{r}
#Inputs and Source Files-------------------------------------

#Inputs
source("Main_Loop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
source("Util_Output_Functions.R")

```

##Running the  Model for Milk.
```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()

source("Main_Loops2.R")
```



```{r}
  #SummaryLisr = List_Sens_Fr
  #FoodType= = "Fruit"
  #1. Start from here
  Individual_Analysis_Fr<-rbind.fill(List_Sens_Pre)
  
  #2. find the dupplicates
  #this step filters replicated based on the ID
  Individual_Analysis_Fr<-Individual_Analysis_Fr %>% 
    group_by(ID) %>% 
    filter(TotServices==max(TotServices))
  #3
  AnalysysDF<-Individual_Analysis_Fr
```

##Start of the Mulk Analysis based on outputs'

###How many Items ended up in which locations
```{r}
library(scales)
library(forcats)

AnalysysDF %>% 
  count(Location) %>% 
  arrange(desc(n)) %>% 
  mutate(Location = fct_reorder(Location, n)) %>%
  ggplot(aes(x =Location, y = n/sum(n)*100))+
  scale_y_continuous(labels = scales::percent_format(scale = 1) )+
  geom_col()+
  labs(x = "Final Food Location", y = "Percent of milk items by location", title= "Final Location for milk-Donation happens end of week")+
  theme(plot.title = element_text(hjust = 0.5))+
  coord_flip()
  
```

###What is the distribution of time for the milk items

```{r}
AnalysysDF %>%
  ggplot(aes(x = TotTime))+
  geom_histogram()+
  scale_x_continuous(n.breaks= 10)+
  labs(x = "Time in Hours", y = "Count ", title= "Time in system by Item week")+
  theme(plot.title = element_text(hjust = 0.5))
  

```

###APC Contamination by Items

```{r}
AnalysysDF %>%
  ggplot(aes(x = SpoilageCon))+
  geom_histogram(color="darkblue", fill="lightblue")+
  geom_vline(xintercept =7, color= "Red")+
  scale_x_continuous(n.breaks= 10)+
  labs(x = "Phsychotroph Population Log CFU/ml", y = "Count", title= "Levels per milk carton")+
  theme(plot.title = element_text(hjust = 0.5))
```

#Relationship between Time and APC Levels
```{r}
AnalysysDF %>% 
  ggplot(aes(y = SpoilageCon, x= TotTime, color = ConsumedAt))+
  geom_point( size =2, fill = "skyblue", shape = 21, alpha = 0.7, fill = "blue")+
  geom_hline(yintercept =7, color= "Red")+
  facet_wrap(.~Location, scales = "free_x")+
  labs(x = "Time in System", y = "Phsychotroph Population Log CFU/ml", title= "Psychotrophic Population vs total time in system, milk Items- Week")+
  scale_y_continuous()+
  scale_x_log10(n.breaks= 10)+
  theme(plot.title = element_text(hjust = 0.5))

```

#Change in Contamination Levels due to Time
  ##Need to figure out a way to track contamination chhange. 
```{r}

```



#
```{r}
Pre_Data_Full %>% 
  filter(Location=="Shared")
```



