---
title: "Untitled"
output: html_document
date: '2022-06-10'
---
#Milk Spoilage working file

## Loading all the libraries.

```{r}
library(tidyverse)
library(ExtDist)
library(jmuOutlier)
library(truncnorm)
library(reshape2)
```

## Fucntions for growth and lag phases 
```{r}
#Function for growth and lag phase
new_growth_rate<-function(newTemp, oldMu,oldTemp = 6, T0 = -4.15){
  newMu<-((newTemp-T0)/(oldTemp-T0))* oldMu
  return (newMu)
}

#Calculation of the new lag time.
new_lag_time <- function (newTemp, oldLag, oldTemp = 6, T0 = -4.15) {
  numerator <- oldTemp -T0
  denom <- newTemp - T0
  newLag <- ( (numerator / denom)^2) * oldLag
  return(newLag)
}


#Automatic Time + Change function
look_for_st<-function(df = SpeciesDF,st, par_of_int){
  if (par_of_int == "lagt"){
    x<-df %>% 
      filter(ST == st) %>% 
      pull(lag_h)
  } else if (par_of_int == "mumax"){
    x<-df %>% 
      filter(ST == st) %>% 
      pull(mumax)
  } else if (par_of_int == "Nmax"){
    x<-df %>% 
      filter(ST == st) %>% 
      pull(Nmax)
  } else if (par_of_int == "GModel"){
    x<-df %>% 
      filter(ST == st) %>% 
      pull(GModel)
  }else {
    stop(paste0(par_of_int, " is not a valid parameter name. Must be one of lagt, mumax, Nmax"))
  }
  return(x)
}

#This function calculates thee growth based on a time and temperature profile for 1 specific milk. 
Func_Growth_LagCon<-function(In_Lag_Consumed, Time_Temp_df,ST_Iter,Interval){
  #In_Lag_Consumed= Total lag time consumed
  #Time_Temp_df = dataframe with time and temperature conditions
  #ST_Iter = The ST that corresponds to this milk carton
  #Interval = time interval in the time_temp_df in hrs. 
  Total_Lag_Consumed<-In_Lag_Consumed
  Total_Growth  <- 0
  old_lag = look_for_st(st= ST_Iter, par_of_int = "lagt")
  old_mumax = look_for_st(st= ST_Iter, par_of_int = "mumax")
  for (i in 1:nrow(Time_Temp_df)){
    if (Total_Lag_Consumed <1 && old_lag!=0){
      Lag_t_interval<-new_lag_time(newTemp = Time_Temp_df$means[i], oldLag = old_lag)
      Lag_Consumed<-Interval/Lag_t_interval
      Total_Lag_Consumed<-Total_Lag_Consumed+Lag_Consumed
      Growth = 0
    } else if (Total_Lag_Consumed>=1 | old_lag == 0){
      Growth = ((new_growth_rate(newTemp = Time_Temp_df$means[i], oldMu = old_mumax))/2.303)*0.684 #Converted log10 from log ln
      Total_Growth = Total_Growth + (Growth*Interval)
    }
  }
  return(c(Total_Growth,Total_Lag_Consumed))
}


#Not in use, function to create a data frame based on interval and initial and final temperature
Time_Temp_Creation<-function(Total_Time, Interval, Initial_Temperature, Final_Temperature){
  Time_Temp_df<-data.frame("min"= seq(0,Total_Time,by = Interval),
                         "means"  = seq(Initial_Temperature,Final_Temperature, by = ((Final_Temperature - Initial_Temperature)/(length(seq(0,Total_Time,by = Interval)) - 1) )))
}

```

## Loading the species df
This chunk loads the species dataframe with the buchanan 3 phase linear model provided by Dr. Murphy
https://www.sciencedirect.com/science/article/pii/S0022030221010900
Uses species from this specific paper. But not the exactdata in the paper since the buchanan 3 phase linear model is used instead. 

```{r}
#Species df in the main fil
SpeciesDF<-read_csv("SpeciesData.csv")
#Prevalences for paper, used to fill out which STs are most common among milks
Prevs<-c(8.93,0.65,1.53,0.87,8.93,0.22,1.31,1.31,0.22,0.22,2.18,2.18)
Prevs<-Prevs/sum(Prevs)
SpeciesDF$Prev<-Prevs
```


## Buchanan Spoilage

This chunk contains the function that iterated through the dataframe based on a time and temperature profile. Calculates the new population of psycho tolerant organism in milk based on the time and temp profile, lag phase consumed and current population. It uses the Buchanan 3 phase linear model, which is slightly conservative at predicting spoilage. 

```{r}
Spoilage_Function<-function(Milkdf,Time_Temp_df){
  for(i in 1:nrow(Milkdf)){
  In_Lag_Consumed<-Milkdf$LagCon[i] #selecting lag for specific milk
  ST_Iter<-Milkdf$Species[i] #selecting the ST of interest
  Pop_Max<-look_for_st(st= ST_Iter,par_of_int = "Nmax") #Population max for given ST

  Interval <- 1/60 #Interval in hours. means 0.01666 hours. maybe need is an input? 
  
  #this function provides two outputs, the total growth, and the new updated lag phase consumed. 
  Output_Milk<-Func_Growth_LagCon(In_Lag_Consumed = In_Lag_Consumed ,Time_Temp_df = Time_Temp_df,ST_Iter = ST_Iter,Interval = Interval)
  
  #updating the total lag consumed
  Milkdf$LagCon[i]<-Output_Milk[2]
  #Updating the spoilage contamination of milk
  Milkdf$SpoilageCon[i]<-Output_Milk[1]+Milkdf$SpoilageCon[i]
  #Updating, that is Pop max is reached, then the current population is at population max. 
  if(Milkdf$SpoilageCon[i]>Pop_Max){
    Milkdf$SpoilageCon[i]<-Pop_Max
  }
  }
  #Returns the updated milk data frame
  return(Milkdf)
}

#DO NOT USE:  this function is trying to make a better version that can be used with apply. Still working on it. 
Spoilage_Function_Apply<-function(Milkdf,Time_Temp_df){
  In_Lag_Consumed<-Milkdf[3] #Lag Con
  ST_Iter<-Milkdf[4] #Species
  Pop_Max<-look_for_st(st= ST_Iter,par_of_int = "Nmax")
  
  Interval <- 1/60
  
  Output_Milk<-Func_Growth_LagCon(In_Lag_Consumed = In_Lag_Consumed ,Time_Temp_df = Time_Temp_df,ST_Iter = ST_Iter,Interval = Interval)
  
  Milkdf[3]<-Output_Milk[2]
  Milkdf[2]<-Output_Milk[1]+Milkdf[2]
  if(Milkdf[2]>Pop_Max){
    Milkdf[2]<-Pop_Max
  }
  return(Milkdf)
}

```

### Small Validation Scenario
Doing small validation scenario to validate model according to the data from the paper. Better validation in the other script. 
Milk Spoilage Working File. 
```{r}
Temperature_Static<- rlaplace(1,m=4.06,s=2.31)
while (Temperature_Static > 15 | Temperature_Static < -1) {
  Temperature_Static<- rlaplace(1,m=4.06,s=2.31)
}
Time_Temp_df<-data.frame("min"= seq(1,1060*5))
Time_Temp_df$means = 4.06


Milkdf<-data.frame("MilkID" = seq(0,100),"SpoilageCon" =NA, "LagCon" = 0, "Species" = NA)
Milkdf$Species<-9#sample(SpeciesDF$ST,size = length(Milkdf$Species), prob = SpeciesDF$Prev, replace = T)
Milkdf$SpoilageCon<-2.1#rtruncnorm(n = length(Milkdf$SpoilageCon),b = 3, mean =0.3817872, sd=1.108859)
Milkdf$SpoilageConIn<-Milkdf$SpoilageCon

mean(Milkdf$SpoilageConIn)

N_Days = 1

for (i in 1:N_Days){
  Milkdf<-Spoilage_Function(Milkdf,Time_Temp_df)
}

mean(Milkdf$SpoilageCon)

```


#Creating the same Milk DF for all
```{r}
Milkdf<-data.frame("MilkID" = seq(0,1000),"SpoilageCon" =NA, "LagCon" = 0, "Species" = NA)
Milkdf$Species<-sample(SpeciesDF$ST,size = length(Milkdf$Species), prob = SpeciesDF$Prev, replace = T)
Milkdf$SpoilageCon<-rtruncnorm(n = length(Milkdf$SpoilageCon),b = 3, mean =0.3817872, sd=1.108859)
Milkdf$SpoilageConIn<-Milkdf$SpoilageCon

mean(Milkdf$SpoilageCon)

Midfbu<-Milkdf

```



```{r}
OvernightSto_C %>% 
  ggplot(aes(x = min, y = means))+
  geom_point()


OvernightSto_C_Ext<-rbind(OvernightSto_C,OvernightSto_C[c(1039:1104),],OvernightSto_C[c(1039:1104),])
OvernightSto_C_Ext$min<-c(1:1308)
OvernightSto_C_Ext<-OvernightSto_C_Ext[c(1:1301),]

OvernightSto_C_Ext %>% 
  ggplot(aes(x = min, y = means))+
  geom_point()


```

```{r}
#Overnight Storage Extended
  
N_Days = 5

Milkdf_ON_FT<-Milkdf

for (i in 1:N_Days){
  #Overnight
  Milkdf_ON_FT<-Spoilage_Function(Milkdf_ON_FT,OvernightSto_C_Ext)
  if (i == 1){
    Milkdf_ON_FT$D1<-Milkdf_ON_FT$SpoilageCon
  } else if (i ==2){
    Milkdf_ON_FT$D2<-Milkdf_ON_FT$SpoilageCon
  } else if (i ==3){
    Milkdf_ON_FT$D3<-Milkdf_ON_FT$SpoilageCon
  }else if (i ==4){
    Milkdf_ON_FT$D4<-Milkdf_ON_FT$SpoilageCon
  }else if (i ==5){
    Milkdf_ON_FT$D5<-Milkdf_ON_FT$SpoilageCon
  }
  print(i)
}


Milkdf_ON_FT_Melted<-melt(Milkdf_ON_FT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_ON_FT_Melted$type<-"Full Time in Fridge"


Milkdf_ON_FT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_ON_FT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_ON_FT$SpoilageCon)
median(Milkdf_ON_FT$SpoilageCon)
quantile(Milkdf_ON_FT$SpoilageCon, c(0.95, 0.05))

#The percentage that are above 20,000 CFU/mL
sum(Milkdf_ON_FT$SpoilageCon>4.30)/(1000)*100

Milkdf_ON_FT$Change  = Milkdf_ON_FT$SpoilageCon-Milkdf_ON_FT$SpoilageConIn

mean(Milkdf_ON_FT$Change)


Milkdf_ON_FT_Melted %>% 
  filter(variable != "SpoilageCon") %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)
  
```




```{r}
#Tray with Ice All Time in Condition
  
N_Days = 5

Milkdf_TI_FT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_TI_FT<-Spoilage_Function(Milkdf_TI_FT,TI_L_FT_L1)
  #Break 1:
  Milkdf_TI_FT<-Spoilage_Function(Milkdf_TI_FT,TI_L_FT_B1)
  #Lunch 2:
  Milkdf_TI_FT<-Spoilage_Function(Milkdf_TI_FT,TI_L_FT_L2) 
  #Overnight
  Milkdf_TI_FT<-Spoilage_Function(Milkdf_TI_FT,OvernightSto_C)
  if (i == 1){
    Milkdf_TI_FT$D1<-Milkdf_TI_FT$SpoilageCon
  } else if (i ==2){
    Milkdf_TI_FT$D2<-Milkdf_TI_FT$SpoilageCon
  } else if (i ==3){
    Milkdf_TI_FT$D3<-Milkdf_TI_FT$SpoilageCon
  }else if (i ==4){
    Milkdf_TI_FT$D4<-Milkdf_TI_FT$SpoilageCon
  }else if (i ==5){
    Milkdf_TI_FT$D5<-Milkdf_TI_FT$SpoilageCon
  }
  print(i)
}

#Milkdf_TI_HT$Change  = Milkdf_TI_HT$SpoilageCon-Milkdf$SpoilageConIn

#mean(Milkdf$Change)

Milkdf_Melted_TI_FT<-melt(Milkdf_TI_FT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_Melted_TI_FT$type<-"Tray with Ice Full Time"


Milkdf_Melted_TI_FT %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_Melted_TI_FT %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_TI_FT$SpoilageCon)
median(Milkdf_TI_FT$SpoilageCon)
quantile(Milkdf_TI_FT$SpoilageCon, c(0.95, 0.05))

#The percentage that are above 20,000 CFU/mL
sum(Milkdf_TI_FT$SpoilageCon>4.30)/(1000)*100

Milkdf_TI_FT$Change  = Milkdf_TI_FT$SpoilageCon-Milkdf_TI_FT$SpoilageConIn

mean(Milkdf_TI_FT$Change)


Milkdf_Melted_TI_FT %>% 
  filter(variable != "SpoilageCon") %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)
  

```

```{r}
#Tray with Ice half condition
  
N_Days = 5

Milkdf_TI_HT<-Milkdf

for (i in 1:N_Days){
   #Service 1:
  Milkdf_TI_HT<-Spoilage_Function(Milkdf_TI_HT,TI_L_HT_L1)
  #Break 1:
  Milkdf_TI_HT<-Spoilage_Function(Milkdf_TI_HT,TI_L_HT_B1)
  #Lunch 2:
  Milkdf_TI_HT<-Spoilage_Function(Milkdf_TI_HT,TI_L_HT_L2) 
  #Overnight
  Milkdf_TI_HT<-Spoilage_Function(Milkdf_TI_HT,OvernightSto_C)
  print(paste("Day", i))
  if (i == 1){
    Milkdf_TI_HT$D1<-Milkdf_TI_HT$SpoilageCon
  } else if (i ==2){
    Milkdf_TI_HT$D2<-Milkdf_TI_HT$SpoilageCon
  } else if (i ==3){
    Milkdf_TI_HT$D3<-Milkdf_TI_HT$SpoilageCon
  }else if (i ==4){
    Milkdf_TI_HT$D4<-Milkdf_TI_HT$SpoilageCon
  }else if (i ==5){
    Milkdf_TI_HT$D5<-Milkdf_TI_HT$SpoilageCon
  }
}


Milkdf_Melted_TI_HT<-melt(Milkdf_TI_HT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_Melted_TI_HT$type<-"Tray with Ice Half Time"

Milkdf_Melted_TI_HT %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_Melted_TI_HT %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_TI_HT$SpoilageCon)
median(Milkdf_TI_HT$SpoilageCon)
quantile(Milkdf_TI_HT$SpoilageCon, c(0.95, 0.05))

#The percentage that are above 20,000 CFU/mL
sum(Milkdf_TI_HT$SpoilageCon>4.30)/(1000)

Milkdf_TI_HT$Change  = Milkdf_TI_HT$SpoilageCon-Milkdf_TI_HT$SpoilageConIn

mean(Milkdf_TI_HT$Change)

```

##Experiment worse case scenario room temp B: 

```{r}
#Full time
N_Days = 5

Milkdf_RTB_FT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_RTB_FT<-Spoilage_Function(Milkdf_RTB_FT,RTB_L_ALL_L1)
  #Break 1:
  Milkdf_RTB_FT<-Spoilage_Function(Milkdf_RTB_FT,RTB_L_ALL_B1)
  #Lunch 2:
  Milkdf_RTB_FT<-Spoilage_Function(Milkdf_RTB_FT,RTB_L_ALL_L2)
  #ON Storage
  Milkdf_RTB_FT<-Spoilage_Function(Milkdf_RTB_FT,OvernightSto_C)
  print(paste("Day", i))
  
  if (i == 1){
    Milkdf_RTB_FT$D1<-Milkdf_RTB_FT$SpoilageCon
  } else if (i ==2){
    Milkdf_RTB_FT$D2<-Milkdf_RTB_FT$SpoilageCon
  } else if (i ==3){
    Milkdf_RTB_FT$D3<-Milkdf_RTB_FT$SpoilageCon
  }else if (i ==4){
    Milkdf_RTB_FT$D4<-Milkdf_RTB_FT$SpoilageCon
  }else if (i ==5){
    Milkdf_RTB_FT$D5<-Milkdf_RTB_FT$SpoilageCon
  }
}

library(reshape2)

Milkdf_RTB_FT_Melted<-melt(Milkdf_RTB_FT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_RTB_FT_Melted$type<-"Room Temp B"

Milkdf_RTB_FT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_RTB_FT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_RTB_FT$SpoilageCon)
median(Milkdf_RTB_FT$SpoilageCon)
quantile(Milkdf_RTB_FT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_RTB_FT$SpoilageCon>4.30)/(1000)

Milkdf_RTB_FT$Change  = Milkdf_RTB_FT$SpoilageCon-Milkdf_RTB_FT$SpoilageConIn

mean(Milkdf_RTB_FT$Change)
  
```



## Room Temp A 

```{r}
#Full time
N_Days = 5

Milkdf_RTA_HT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_RTA_HT<-Spoilage_Function(Milkdf_RTA_HT,RTA_L_ALL_L1)
  #Break 1:
  Milkdf_RTA_HT<-Spoilage_Function(Milkdf_RTA_HT,RTA_L_ALL_B1)
  #Lunch 2:
  Milkdf_RTA_HT<-Spoilage_Function(Milkdf_RTA_HT,RTA_L_ALL_L2)
  #ON Storage
  Milkdf_RTA_HT<-Spoilage_Function(Milkdf_RTA_HT,OvernightSto_C)
  print(paste("Day", i))
  
  if (i == 1){
    Milkdf_RTA_HT$D1<-Milkdf_RTA_HT$SpoilageCon
  } else if (i ==2){
    Milkdf_RTA_HT$D2<-Milkdf_RTA_HT$SpoilageCon
  } else if (i ==3){
    Milkdf_RTA_HT$D3<-Milkdf_RTA_HT$SpoilageCon
  }else if (i ==4){
    Milkdf_RTA_HT$D4<-Milkdf_RTA_HT$SpoilageCon
  }else if (i ==5){
    Milkdf_RTA_HT$D5<-Milkdf_RTA_HT$SpoilageCon
  }
}

library(reshape2)

Milkdf_RTA_HT_Melted<-melt(Milkdf_RTA_HT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_RTA_HT_Melted$type<-"Room Temp A"

Milkdf_RTA_HT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_RTA_HT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_RTA_HT$SpoilageCon)
median(Milkdf_RTA_HT$SpoilageCon)
quantile(Milkdf_RTA_HT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_RTA_HT$SpoilageCon>4.30)/(1000)

Milkdf_RTA_HT$Change  = Milkdf_RTA_HT$SpoilageCon-Milkdf_RTA_HT$SpoilageConIn

mean(Milkdf_RTA_HT$Change)
  
```


## Worse case scenario Ref Tray
```{r}
#Long FT in Condition

N_Days = 5

Milkdf_RefT_FT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_RefT_FT<-Spoilage_Function(Milkdf_RefT_FT,RefT_L_FT_L1)
  #Break 1:
  Milkdf_RefT_FT<-Spoilage_Function(Milkdf_RefT_FT,RefT_L_FT_B1)
  #Lunch 2:
  Milkdf_RefT_FT<-Spoilage_Function(Milkdf_RefT_FT,RefT_L_FT_B1)
  #ON Storage
  Milkdf_RefT_FT<-Spoilage_Function(Milkdf_RefT_FT,OvernightSto_C)
  print(paste("Day", i))

  if (i == 1){
   Milkdf_RefT_FT$D1<-Milkdf_RefT_FT$SpoilageCon
  } else if (i ==2){
    Milkdf_RefT_FT$D2<-Milkdf_RefT_FT$SpoilageCon
  } else if (i ==3){
    Milkdf_RefT_FT$D3<-Milkdf_RefT_FT$SpoilageCon
  }else if (i ==4){
    Milkdf_RefT_FT$D4<-Milkdf_RefT_FT$SpoilageCon
  }else if (i ==5){
    Milkdf_RefT_FT$D5<-Milkdf_RefT_FT$SpoilageCon
  }
}


Milkdf_RefT_FT_Melted<-melt(Milkdf_RefT_FT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_RefT_FT_Melted$type<-"Refrigerated Tray Full Time"

Milkdf_RefT_FT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_RefT_FT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_RefT_FT$SpoilageCon)
median(Milkdf_RefT_FT$SpoilageCon)
quantile(Milkdf_RefT_FT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_RefT_FT$SpoilageCon>4.30)/(1000)

Milkdf_RefT_FT$Change  = Milkdf_RefT_FT$SpoilageCon-Milkdf_RefT_FT$SpoilageConIn

mean(Milkdf_RefT_FT$Change)

```


```{r}
#Long Half Time in Condition

N_Days = 5

Milkdf_RefT_HT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_RefT_HT<-Spoilage_Function(Milkdf_RefT_HT,RefT_L_HT_L1)
  #Break 1:
  Milkdf_RefT_HT<-Spoilage_Function(Milkdf_RefT_HT,RefT_L_HT_B1)
  #Lunch 2:
  Milkdf_RefT_HT<-Spoilage_Function(Milkdf_RefT_HT,RefT_L_HT_B1)
  #ON Storage
  Milkdf_RefT_HT<-Spoilage_Function(Milkdf_RefT_HT,OvernightSto_C)
  print(paste("Day", i))
  
  if (i == 1){
   Milkdf_RefT_HT$D1<-Milkdf_RefT_HT$SpoilageCon
  } else if (i ==2){
    Milkdf_RefT_HT$D2<-Milkdf_RefT_HT$SpoilageCon
  } else if (i ==3){
    Milkdf_RefT_HT$D3<-Milkdf_RefT_HT$SpoilageCon
  }else if (i ==4){
    Milkdf_RefT_HT$D4<-Milkdf_RefT_HT$SpoilageCon
  }else if (i ==5){
    Milkdf_RefT_HT$D5<-Milkdf_RefT_HT$SpoilageCon
  }
}


Milkdf_RefT_HT_Melted<-melt(Milkdf_RefT_HT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_RefT_HT_Melted$type<-"Refrigerated Tray Half Time"

Milkdf_RefT_HT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_RefT_HT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_RefT_HT$SpoilageCon)
median(Milkdf_RefT_HT$SpoilageCon)
quantile(Milkdf_RefT_HT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_RefT_HT$SpoilageCon>4.30)/(1000)

Milkdf_RefT_HT$Change  = Milkdf_RefT_HT$SpoilageCon-Milkdf_RefT_HT$SpoilageConIn

mean(Milkdf_RefT_HT$Change)

```


## Tray with Ice Packs
```{r}
#Long FT in Condition

N_Days = 5

Milkdf_TIP_FT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_TIP_FT<-Spoilage_Function(Milkdf_TIP_FT,TIP_L_FT_L1)
  #Break 1:
  Milkdf_TIP_FT<-Spoilage_Function(Milkdf_TIP_FT,TIP_L_FT_B1)
  #Lunch 2:
  Milkdf_TIP_FT<-Spoilage_Function(Milkdf_TIP_FT,TIP_L_FT_B1)
  #ON Storage
  Milkdf_TIP_FT<-Spoilage_Function(Milkdf_TIP_FT,OvernightSto_C)
  print(paste("Day", i))
  
  if (i == 1){
   Milkdf_TIP_FT$D1<-Milkdf_TIP_FT$SpoilageCon
  } else if (i ==2){
    Milkdf_TIP_FT$D2<-Milkdf_TIP_FT$SpoilageCon
  } else if (i ==3){
    Milkdf_TIP_FT$D3<-Milkdf_TIP_FT$SpoilageCon
  }else if (i ==4){
    Milkdf_TIP_FT$D4<-Milkdf_TIP_FT$SpoilageCon
  }else if (i ==5){
    Milkdf_TIP_FT$D5<-Milkdf_TIP_FT$SpoilageCon
  }
}


Milkdf_TIP_FT_Melted<-melt(Milkdf_TIP_FT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_TIP_FT_Melted$type<-"Tray with Ice Packs Full Time"

Milkdf_TIP_FT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_TIP_FT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_TIP_FT$SpoilageCon)
median(Milkdf_TIP_FT$SpoilageCon)
quantile(Milkdf_TIP_FT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_TIP_FT$SpoilageCon>4.30)/(1000)

Milkdf_TIP_FT$Change  = Milkdf_TIP_FT$SpoilageCon-Milkdf_TIP_FT$SpoilageConIn

mean(Milkdf_TIP_FT$Change)

```


```{r}
#Long HT in Condition

N_Days = 5

Milkdf_TIP_HT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_TIP_HT<-Spoilage_Function(Milkdf_TIP_HT,TIP_L_HT_L1)
  #Break 1:
  Milkdf_TIP_HT<-Spoilage_Function(Milkdf_TIP_HT,TIP_L_HT_B1)
  #Lunch 2:
  Milkdf_TIP_HT<-Spoilage_Function(Milkdf_TIP_HT,TIP_L_HT_B1)
  #ON Storage
  Milkdf_TIP_HT<-Spoilage_Function(Milkdf_TIP_HT,OvernightSto_C)
  print(paste("Day", i))
    if (i == 1){
   Milkdf_TIP_HT$D1<-Milkdf_TIP_HT$SpoilageCon
  } else if (i ==2){
    Milkdf_TIP_HT$D2<-Milkdf_TIP_HT$SpoilageCon
  } else if (i ==3){
    Milkdf_TIP_HT$D3<-Milkdf_TIP_HT$SpoilageCon
  }else if (i ==4){
    Milkdf_TIP_HT$D4<-Milkdf_TIP_HT$SpoilageCon
  }else if (i ==5){
    Milkdf_TIP_HT$D5<-Milkdf_TIP_HT$SpoilageCon
  }
}


Milkdf_TIP_HT_Melted<-melt(Milkdf_TIP_HT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_TIP_HT_Melted$type<-"Tray with Ice Packs Half Time"

Milkdf_TIP_HT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_TIP_HT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_TIP_HT$SpoilageCon)
median(Milkdf_TIP_HT$SpoilageCon)
quantile(Milkdf_TIP_HT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_TIP_HT$SpoilageCon>4.30)/(1000)

Milkdf_TIP_HT$Change  = Milkdf_TIP_HT$SpoilageCon-Milkdf_TIP_HT$SpoilageConIn

mean(Milkdf_TIP_HT$Change)

```



## Cooler with Ice
```{r}
#Long FT in Condition

N_Days = 5

Milkdf_CI_FT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_CI_FT<-Spoilage_Function(Milkdf_CI_FT,CI_L_FT_L1)
  #Break 1:
  Milkdf_CI_FT<-Spoilage_Function(Milkdf_CI_FT,CI_L_FT_B1)
  #Lunch 2:
  Milkdf_CI_FT<-Spoilage_Function(Milkdf_CI_FT,CI_L_FT_B1)
  #ON Storage
  Milkdf_CI_FT<-Spoilage_Function(Milkdf_CI_FT,OvernightSto_C)
  print(paste("Day", i))
  
  if (i == 1){
   Milkdf_CI_FT$D1<-Milkdf_CI_FT$SpoilageCon
  } else if (i ==2){
    Milkdf_CI_FT$D2<-Milkdf_CI_FT$SpoilageCon
  } else if (i ==3){
    Milkdf_CI_FT$D3<-Milkdf_CI_FT$SpoilageCon
  }else if (i ==4){
    Milkdf_CI_FT$D4<-Milkdf_CI_FT$SpoilageCon
  }else if (i ==5){
    Milkdf_CI_FT$D5<-Milkdf_CI_FT$SpoilageCon
  }
}


Milkdf_CI_FT_Melted<-melt(Milkdf_CI_FT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_CI_FT_Melted$type<-"Cooler with Ice Full Time"

Milkdf_CI_FT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_CI_FT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_CI_FT$SpoilageCon)
median(Milkdf_CI_FT$SpoilageCon)
quantile(Milkdf_CI_FT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_CI_FT$SpoilageCon>4.30)/(1000)

Milkdf_CI_FT$Change  = Milkdf_CI_FT$SpoilageCon-Milkdf_CI_FT$SpoilageConIn

mean(Milkdf_CI_FT$Change)

```

```{r}
#Long HT in Condition

N_Days = 5

Milkdf_CI_HT<-Milkdf

for (i in 1:N_Days){
  #Service 1:
  Milkdf_CI_HT<-Spoilage_Function(Milkdf_CI_HT,CI_L_HT_L1)
  #Break 1:
  Milkdf_CI_HT<-Spoilage_Function(Milkdf_CI_HT,CI_L_HT_B1)
  #Lunch 2:
  Milkdf_CI_HT<-Spoilage_Function(Milkdf_CI_HT,CI_L_HT_B1)
  #ON Storage
  Milkdf_CI_HT<-Spoilage_Function(Milkdf_CI_HT,OvernightSto_C)
  print(paste("Day", i))
  
  if (i == 1){
   Milkdf_CI_HT$D1<-Milkdf_CI_HT$SpoilageCon
  } else if (i ==2){
    Milkdf_CI_HT$D2<-Milkdf_CI_HT$SpoilageCon
  } else if (i ==3){
    Milkdf_CI_HT$D3<-Milkdf_CI_HT$SpoilageCon
  }else if (i ==4){
    Milkdf_CI_HT$D4<-Milkdf_CI_HT$SpoilageCon
  }else if (i ==5){
    Milkdf_CI_HT$D5<-Milkdf_CI_HT$SpoilageCon
  }
}


Milkdf_CI_HT_Melted<-melt(Milkdf_CI_HT, id.vars = c("MilkID", "LagCon", "Species"))
Milkdf_CI_HT_Melted$type<-"Cooler with Ice Half Time"

Milkdf_CI_HT_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= variable))+
  geom_density( alpha = 0.5)

Milkdf_CI_HT_Melted %>% 
  ggplot(aes(y =value , group= variable, x= variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

mean(Milkdf_CI_HT$SpoilageCon)
median(Milkdf_CI_HT$SpoilageCon)
quantile(Milkdf_CI_HT$SpoilageCon, c(0.95, 0.05))

sum(Milkdf_CI_HT$SpoilageCon>4.30)/(1000)

Milkdf_CI_HT$Change  = Milkdf_CI_HT$SpoilageCon-Milkdf_CI_HT$SpoilageConIn

mean(Milkdf_CI_HT$Change)

```


```{r}
summary_func<-function(df){
  df %>% 
  group_by(variable) %>% 
  summarise(mean = mean(value),
            q5 = quantile(value, 0.05),
            q95 = quantile(value, 0.95),
            spoiled = ((sum(value>log10(20000)))/1000)*100)
}

summary_func(Milkdf_ON_FT_Melted)
summary_func(Milkdf_RTB_FT_Melted)
summary_func(Milkdf_RTA_HT_Melted)
summary_func(Milkdf_Melted_TI_HT)
summary_func(Milkdf_Melted_TI_FT)
summary_func(Milkdf_RefT_HT_Melted)
summary_func(Milkdf_RefT_FT_Melted)
summary_func(Milkdf_TIP_HT_Melted)
summary_func(Milkdf_TIP_FT_Melted)
summary_func(Milkdf_CI_HT_Melted)
summary_func(Milkdf_CI_FT_Melted)

```



#Plotting the comparisons

```{r}
All_Combined_Plots<-rbind(Milkdf_ON_FT_Melted,Milkdf_RTB_FT_Melted, Milkdf_RTA_HT_Melted, Milkdf_Melted_TI_FT, Milkdf_Melted_TI_HT,Milkdf_RefT_FT_Melted,Milkdf_RefT_HT_Melted,
      Milkdf_TIP_HT_Melted,Milkdf_TIP_FT_Melted,Milkdf_CI_HT_Melted,Milkdf_CI_FT_Melted )

unique(All_Combined_Plots$type)


Initial_1<-All_Combined_Plots[c(1002:2002),]
Initial_1$type<-"Initial"
Initial_1$variable<-"SpoilageCon"

median(Initial_1$value)

All_Combined_Plots<-rbind(All_Combined_Plots,Initial_1)

All_Combined_Plots$type<-factor(All_Combined_Plots$type, levels = c("Initial","Full Time in Fridge","Room Temp B","Room Temp A","Tray with Ice Half Time","Tray with Ice Full Time","Refrigerated Tray Half Time" ,"Refrigerated Tray Full Time","Tray with Ice Packs Half Time","Tray with Ice Packs Full Time","Cooler with Ice Half Time","Cooler with Ice Full Time"))

All_Combined_Plots$variable<-factor(All_Combined_Plots$variable, levels = c("SpoilageConIn", "D1", "D2", "D3", "D4", "D5", "SpoilageCon"))


All_Combined_Plots %>%
  filter(variable == "SpoilageCon") %>% 
  ggplot(aes(y =value, x = type))+
  geom_point(position = "jitter", alpha = 0.1)+
  geom_boxplot(alpha = 0.8)+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)+
  geom_hline(yintercept =  1.56494, color = "blue", size = 1, alpha = 0.7, linetype='dashed')+
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  labs(x = "Condition Type")


All_Combined_Plots %>%
  filter(variable != "SpoilageCon") %>% 
  ggplot(aes(y =value, x = variable))+
  geom_point(position = "jitter", alpha = 0.03)+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)+
  geom_hline(yintercept = 1.908454, color = "green", size = 0.7, alpha = 0.9, linetype='dashed')+
  geom_hline(yintercept = 0.3388, color = "blue", size = 0.7, alpha = 0.9, linetype='dashed')+
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  labs(x = "Condition Type")+
  facet_wrap(~type)


All_Combined_Plots %>%
  filter(variable != "SpoilageCon") %>% 
  ggplot(aes(y =value, x = type, fill = variable))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)+
  geom_hline(yintercept = 1.63, color = "blue", size = 1, alpha = 0.7, linetype='dashed')+
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  labs(x = "Condition Type")

All_Combined_Plots %>% 
  group_by(variable) %>% 
  count()



```


```{r}
OvernightSto_C_Ext$treatment<-"Fridge"
OvernightSto_C_Ext$Period<-"Fridge"

names(OvernightSto_C_Ext)
names(RTB_L_ALL)
All_Temperatures_Combined<-rbind(OvernightSto_C_Ext, RTB_L_ALL,RTA_L_ALL,TI_L_FT,RefT_L_FT,TIP_L_FT,CI_L_FT, TI_L_HT, RefT_L_HT,TIP_L_HT,CI_L_HT)

All_Temperatures_Combined$condition<-factor(All_Temperatures_Combined$condition, levels =c("Overnight Storage", "Room Temp B", "Room Temp A", "Tray with Ice", "Refrigerated Tray", "Tray with Ice Packs", "Cooler with Ice"))

All_Temperatures_Combined %>% 
  ggplot(aes(x = min, y = means, color = Period, shape = treatment))+
  #geom_point()+
  geom_line(size = 1.2)+
  facet_wrap(~condition, scales = "free_x")
  
```



```{r}
0.5/1.1
```




















################################################################## 

```{r}
Milkdf<-data.frame("MilkID" = seq(0,100),"SpoilageCon" =NA, "LagCon" = 0, "Species" = NA)
Milkdf$Species<-sample(SpeciesDF$ST,size = length(Milkdf$Species), prob = SpeciesDF$Prev, replace = T)
Milkdf$SpoilageCon<-rtruncnorm(n = length(Milkdf$SpoilageCon),b = 3, mean =0.3817872, sd=1.108859)
Milkdf$SpoilageConIn<-Milkdf$SpoilageCon


N_Days = 1


for (i in 1:N_Days){
  #Service 1:
  Milkdf<-t(as.data.frame(apply(Milkdf,1,Spoilage_Function_Apply, Time_Temp_df = RTB_L_NT_L1)))
  #Break 1:
  Milkdf<-t(as.data.frame(apply(Milkdf,1,Spoilage_Function_Apply, Time_Temp_df = RTB_L_NT_B1)))
  #Lunch 2:
  Milkdf<-t(as.data.frame(apply(Milkdf,1,Spoilage_Function_Apply, Time_Temp_df = RTB_L_NT_L2)))
  #ON Storage
  Milkdf<-  Milkdf<-t(as.data.frame(apply(Milkdf,1,Spoilage_Function_Apply, Time_Temp_df = OvernightSto_C)))
  print(paste("Day", i))
}

library(reshape2)

Milkdf_Melted<-melt(Milkdf, id.vars = c("MilkID", "LagCon", "Species"))

Milkdf_Melted %>% 
  ggplot(aes(x =value, group= variable, fill= Var2))+
  geom_density( alpha = 0.5)

Milkdf_Melted %>% 
  ggplot(aes(y =value , group= Var2, x= Var2))+
  geom_boxplot()+
  labs(y = "log CFU/mL")+
  geom_hline(yintercept = 4.30, color = "red", size = 1)

```


