---
title: "Spoilage Model Validations"
author: "Gustavo Reyes"
date: "11/10/2021"
output: html_document
---
#Validation of spoilage Model

##Shaffner:
Monte Carlo Simulation of the Shelf Life of Pasteurized Milk as Affected by Temperature and Initial Concentration of Spoilage Organisms
###Psychotrophic Organisms: 
```{r}
#Validation of their model, obtaining similar Histograms as theirs for spoilage
shelf_life<-c()
for (i in 1:1000){
  Temp<-rnorm(1,4.4,2)
  Growth_variability <- 1-(rnorm(1,0,17)/100)
  Initial_pop <- rtriang(1,0,1,4)
  GrowthNeedforspoilage<-7-Initial_pop
  Tmin <- -1.19
  bval <-0.03578
  growthRate <- ((Temp-Tmin)*bval)^2
  Adjusted_GrowthRate<-growthRate+Growth_variability
  LogGrowthRate<-Adjusted_GrowthRate*log10(2)
  
  Shelflifedays<-(GrowthNeedforspoilage/LogGrowthRate)
  shelf_life<-c(shelf_life,Shelflifedays)
}

hist(shelf_life,breaks = 100)
abline(v=14, col = "red")
mean(shelf_life)




```

##Sabani
#Simlating APC Spoilage
Sabani et al
Monitoring Shelf Life of Pasteurized Whole MilkUnder Refrigerated Storage Conditions:Predictive Models for Quality Loss
```{r}

log10(2)

10^3

log10(1000)

log(1000)/2.303

```


#Torres Model for both P Putida and L.Monocytogenes
```{r}

#P Putida
bval = 0.03347 #+-0.0002
T_min = -7.7
Coef= 0.1719#+-1.22 C
Tmax<-41.2

Temp<-5

#rate= ((bval*(Temp-T_min))*(1-exp(Coef*(Temp-Tmax))))^(2/2.303)
rate = (bval*(Temp-T_min))^2
print(rate)
adrate = rate/log(10)
print(adrate)
adrate2 = rate*log(2)
print(adrate2)

Time = 175

(adrate*Time)


#Validation

Initial = 4.01
Final = 
Fina-Initial


log(2)


```

Neumeyer
```{r}

bval <- 0.03347 #+-0.0002
T_min <- -7.7

Time<-24
Temp<- 4
rate = (bval*(Temp-T_min))^2/2.303
rate
LagTime = 1/rate
LagTime

Temp = 25
Time = 24
rate = 0.1709*(Temp+6.1)*(1-exp(0.1723*(Temp-41.2)))*(0.996-0.977)
rate = 0.1539*(Temp+7.6)*(0.996-0.947)
rate*Time

lagtime = 1/((bval*(Temp-T_min))^2)

Spoilage<-rate*Time



```


```{r}
#Ratworsky
bval <-0.023
Tmin <--5.647
Temp<-10
ratemax<-(bval*(Temp-T_min))^2/2.303
ratemax

sqrtrate<-c()
Timeseq<-seq(-5,35)
for (i in Timeseq){
  ratemax<-(bval*(i-T_min))
  sqrtrate<-c(sqrtrate,ratemax)
}


plot(x = Timeseq, y = sqrtrate)

1/0.035

1/1.1

```



